BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-06-28 arxiv.Rnw
Updated files for arXiv.
Finished major work on ODD. Ready for proofreading and then I think it's done.

<<setup, echo=F, results='hide', cache=F>>=
library(ggplot2)
library(pander)
source("utils/multi_plot.R")
theme_set(theme_classic())
@

  \usepackage{latexsym}
  \usepackage{graphicx}
  \usepackage{mathptmx}
  \usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
  \usepackage{mhchem}

\bibliographystyle{wsc}

>>>>

<<setup, echo=F, results='hide', cache=F>>=
library(jgplot2) # devtools::install_github('jonathan-g/jgplot2', ref='jgplot2')
library(pander)
source("utils/multi_plot.R")
theme_set(theme_classic())
@

  \usepackage[margin=1in]{geometry}
  \usepackage{latexsym}
  \usepackage{graphicx}
  \usepackage{mathptmx}
  \usepackage{hyperref}
  \usepackage{mhchem}

\hypersetup{colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black}

\input{wscbib}
\bibliographystyle{wsc}

### 2016-06-28 paper.Rmd
Finished major work on ODD. Ready for proofreading and then I think it's done.

---
title: 'Betting and Belief: Prediction Markets and Attribution of Climate Change'
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "March 23, 2016"
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
bibliography: library.bib
---
```{r fig_ref, echo=FALSE}
source("utils/fig_ref.R") # tabRef and figRef functions
source("utils/multi_plot.R")
``` 
```{r, caption_setting, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption">',options$htmlcap,"</p>",sep="")
    }
    })
# small margins
knit_hooks$set(small_mar = function(before, options, envir) {
    if (before) par(mar = rep(0.0001, 4))  # smaller margins all around
})
# opts_chunk$set(dev="tiff", 
#                dev.args=list(compression="lzw", type="cairo"),
#                dpi=300)
```
```{r multi_plot, echo=FALSE}
source("utils/multi_plot.R")
library(ggplot2)
theme_set(theme_classic())
library(pander)
```

>>>>

---
title: 'Betting and Belief: Prediction Markets and Attribution of Climate Change'
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "March 23, 2016"
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
bibliography: library.bib
---
```{r fig_ref, echo=FALSE}
source("utils/fig_ref.R") # tabRef and figRef functions
source("utils/multi_plot.R")
``` 
```{r, caption_setting, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption">',options$htmlcap,"</p>",sep="")
    }
    })
# small margins
knit_hooks$set(small_mar = function(before, options, envir) {
    if (before) par(mar = rep(0.0001, 4))  # smaller margins all around
})
# opts_chunk$set(dev="tiff", 
#                dev.args=list(compression="lzw", type="cairo"),
#                dpi=300)
```
```{r multi_plot, echo=FALSE}
source("utils/multi_plot.R")
# replace ggplot2 with jgplot2 that has my enhancement for outlier.alpha on geom_boxplot.
# library(ggplot2)
library(jgplot2) # devtools::install_github('jonathan-g/jgplot2', ref='jgplot2')
theme_set(theme_classic())
library(pander)
```

### 2016-06-28 prediction_market_wsc.Rnw
Finished major work on ODD. Ready for proofreading and then I think it's done.

<<setup, echo=F, results='hide', cache=F>>=
library(ggplot2)
library(pander)
source("utils/multi_plot.R")
theme_set(theme_classic())
@

>>>>

<<setup, echo=F, results='hide', cache=F>>=
# replace ggplot2 with jgplot2 that has my enhancement for outlier.alpha on geom_boxplot.
# library(ggplot2)
library(jgplot2) # devtools::install_github('jonathan-g/jgplot2', ref='jgplot2')
library(pander)
source("utils/multi_plot.R")
theme_set(theme_classic())
@
